---
title: "Orçun Gümüş's CV"
author: Orcun Gumus
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/styles.css', 'resume']
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results = "asis", 
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)

library(tidyverse)
library(readxl)
library(magick)
library(glue)
library(janitor)
library(bib2df)

source("parse-citations.R")
```

```{css, echo=FALSE}
.pagedjs_page:not(:first-of-type) {
  --sidebar-width: 0rem;
  --sidebar-background-color: #ffffff;
  --main-width: calc(var(--content-width) - var(--sidebar-width));
  --decorator-horizontal-margin: 0.2in;
}
```

# Aside

```{r logo, warning = FALSE, message = FALSE, error = FALSE, out.width="100%"}
logo <- image_read("https://www.verikafasi.org/data/pp.png")
ht <- image_info(logo) %>% pull(height)
wd <- image_info(logo) %>% pull(width)
scale <- 1.5

image_blank(width = wd * scale, height = ht, "hotpink") %>%
  image_composite(logo, offset = paste0("+", ((wd * scale) - wd) / 2, "+0")) %>%
  image_transparent("hotpink", fuzz = 15)
```

## Contact {#contact}

-   <i class="fa fa-envelope"></i> [orcungumus\@gmail.com](mailto:orcungumus@gmail.com){.email}
-   <i class="fa fa-link"></i> [verikafasi.org](https://verikafasi.org)
-   <i class="fa fa-linkedin"></i> [\@guemues](https://linkedin.com/in/guemues)
-   <i class="fa fa-twitter"></i> [\@orcungumus](https://twitter.com/orcungumus)

## Skills {#skills}

**Programming:**

-   Python
-   R
-   SQL
-   Stan

**Interests:**

-   Timeseries
-   Optimization
-   Graph theory
-   Probabilistic programming
-   Causal inference
-   Reinforcement learning
-   Bayesian statistics
-   Generalized linear models
-   Multilevel models


**Software:**

-   Docker
-   Kubernetes
-   Git
-   Tableau

**Languages:**

-   Turkish (Native)
-   English (IELTS 7)
-   French (Intermediate)


## Disclaimer {#disclaimer}

Template forked from [**wjakethompson**](https://github.com/wjakethompson/cv)

Last updated on `r Sys.Date()`

# Main

## Orçun Gümüş {#title}

### Data Science Consultant

## Education {data-icon="graduation-cap" data-concise="true"}

```{r print-edu}
edu_data <- read_xlsx("cv-data.xlsx", sheet = "education")

edu_data %>% 
    arrange(desc(end)) %>% 
    mutate(id = 1:n()) %>% 
    pivot_longer(
      starts_with('description'),
      names_to = 'description_num',
      values_to = 'description',
      values_drop_na = FALSE
    ) %>% 
    filter(!is.na(description) | (description_num == "description_1")) %>%
    group_by(id) %>% 
    mutate(
      descriptions = list(description)
    ) %>% 
    ungroup() %>% 
    filter(description_num == 'description_1') %>% 
    mutate(
      timeline = ifelse(
        is.na(start) | start == end,
        end,
        glue('{end} - {start}')
      ),
      description_bullets = map_chr(descriptions, ~paste('-', ., collapse = '\n')),
    ) %>% 
    mutate(description_bullets = ifelse(description_bullets == "- NA", "", description_bullets)) %>% 
    mutate_all(~ifelse(is.na(.), 'N/A', .)) %>% 
    glue_data(
      "### {title}",
      "\n\n",
      "{institution}",
      "\n\n",
      "{loc}",
      "\n\n",
      "{timeline}", 
      "\n\n",
      "{description_bullets}",
      "\n\n\n",
    )
```

## Employment {data-icon="suitcase"}

```{r print-emp}
emp_data <- read_xlsx("cv-data.xlsx", sheet = "employment")

emp_data %>%
  replace_na(list(end = "present")) %>%
  # mutate_at(vars(start, end), str_replace_all, pattern = "-[0-9]*$", "") %>%
  nest(data = -c(org, institution, loc)) %>%
  mutate(print_data = map(data, function(x) {
    
    current <- filter(x, main == "TRUE")
    previous <- filter(x, main != "TRUE")
    
    prev_positions <- x %>%
      select(title:end) %>%
      separate(start, c("start_year", "start_month"), "-", convert = TRUE) %>%
      separate(end, c("end_year", "end_month"), "-", convert = TRUE,
               fill = "right") %>%
      mutate(start_month = month.name[start_month],
             end_month = map_chr(end_month, function(x) {
               if (is.na(x)) return(NA_character_)
               month.name[x]
             }),
             label = glue("{title} ({start_month} {start_year}--{end_month} {end_year})")) %>%
      pull(label) %>%
      str_replace_all("NA ", "") %>%
      as.character() %>%
      list()
    
    current %>%
      pivot_longer(contains("description"), names_to = "description_num",
                   values_to = "description") %>%
      filter(!is.na(description)) %>%
      group_by(title) %>%
      mutate(descriptions = list(description)) %>%
      ungroup() %>%
      filter(description_num == "description_1") %>%
      mutate(full_start = min(x$start)) %>%
      mutate(full_end = ifelse(end == "present", full_start, end)) %>%
      separate(full_start, c("start_year", "start_month"), convert = TRUE) %>%
      separate(full_end, c("end_year", "end_month"), convert = TRUE) %>%
      mutate(timeline = ifelse(end == "present", glue("{end} - {start_year}"), ifelse(end_year != start_year, glue("{end_year} - {start_year}"), glue("{start_year}")) )) %>%
      mutate(timeline = as.character(timeline),
             description_bullets = map_chr(descriptions, ~paste("-", .x, collapse = "\n")),
             prev_pos = ifelse(nrow(previous) == 0, NA_character_,
                               paste("**Position History**\n\n",
                                     map_chr(prev_positions, ~paste("-", .x, collapse = "\n"))))) %>%
      select(title, timeline, description_bullets, prev_pos)
  })) %>%
  select(-data) %>%
  unnest(cols = c(print_data)) %>%
  glue_data(
    "### {org}{ifelse(is.na(institution), '', paste(',', institution))}",
    "\n\n",
    "{title}",
    "\n\n",
    "{loc}",
    "\n\n",
    "{timeline}",
    "\n\n",
    "{ifelse(description_bullets == '- FALSE', '', description_bullets)}",
    "\n\n",
    "{ifelse(is.na(prev_pos), '', prev_pos)}",
    "\n\n\n"
  )
```

## Publications {data-icon="book"}

```{r print-pub}
format_bib("bib/pubs.bib") %>%
  mutate(across(where(is.character), ~str_replace_all(.x, "\\{|\\}", "")),
         author = map_chr(author, all_authors),
         year = as.integer(year),
         month = as.integer(month)) %>%
  arrange(desc(year), desc(month), author) %>%
  group_by(year) %>%
  mutate(count = 1:n()) %>%
  ungroup() %>%
  mutate(year = case_when(count != 1 ~ "N/A", TRUE ~ as.character(year))) %>%
  glue_data(
    "### {title}",
    "\n\n",
    "{citation}",
    "\n\n",
    "N/A",
    "\n\n",
    "{year}",
    "\n\n\n"
  )
```

## Teaching Assistantships {data-icon="users"}

### Internet Analytics, Swiss Federal Institute of Technology in Lausanne
A course about graph processing, recommender systems,clustering and PCA <i class="fa fa-link"></i> [EPFL Course Link](https://edu.epfl.ch/coursebook/en/internet-analytics-COM-308)

N/A

2018


### Large Scale Data Analysis, Bilkent University
A courseabout Markov chains, PageRank, Map Reduce and collaborative filtering <i class="fa fa-link"></i> [Bilkent Course Link](http://www.cs.bilkent.edu.tr/~mustafa.ozdal/cs425/index_Fall2015.html)

N/A

2016


## Awards and service {data-icon="award"}

```{r print-awds}
awd_data <- read_xlsx("cv-data.xlsx", sheet = "awards")

awards <- awd_data %>%
  filter(display) %>%
  mutate(date = case_when(is.na(end_date) ~ as.character(start_date),
                          TRUE ~ paste0(start_date, "--", end_date)),
         display_text = glue("- {award} ({date})"),
         status = "Professional Awards") %>%
  group_by(status) %>%
  summarize(bullets = paste(display_text, collapse = "\n"))



awards %>%
  mutate(status = factor(status,
                         levels = c("Currently Funded",
                                    "Under Review",
                                    "Previously Funded",
                                    "Unfunded",
                                    "Professional Awards"),
                         labels = c("Currently Funded Grants",
                                    "Grants Under Review",
                                    "Previously Funded Grants",
                                    "Unfunded Grants",
                                    "Professional Awards"))) %>%
  arrange(status) %>%
  glue_data(
    "### {status}",
    "\n\n",
    "{bullets}",
    "\n\n",
    "N/A",
    "\n\n\n"
  )

```

### Transparency International 

Project owner for democratization city plans using recent technological developments

N/A

2020

### Bilkent Eurogame Entertainment Club

President of biggest Eurogame entertainment club in Turkey

N/A

2013 - 2017

- Increased organization budget by 300% through the nationwide events and establishing a network of sponsors

